---
title: "thlGraphs Vignette Colors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{thlGraphs Vignette Colors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  warning = FALSE,
  fig.width = 7, 
  fig.height = 1
)
library(thlGraphs)
```

## Demostration of using THL's colors

`thlGraphs` defines colors, color palettes and color sets matching THL's visual guidelines and graphical theme.

Colors are named as well the palettes.

### Color names

Picking single colors is done by referring them by their name in `colors_thl()`.
`colornames_thl` lists all predefined color names.
Names are defined both in English and in Finnish.

Displaying both English and Finnish main color names:

```{r}
colornames_thl()
```

`thlGraphs` also defines many secondary colors which are tinted versions of the main colors. 
These colors can be found eg. in continuous color palettes.
Names for these can be found with `colornames_thl(include.secondary = TRUE)`


### Usage of colors and color names

In following examples we pick some of these colors and preview them as plot.

`colors_thl()` returns colors' corresponding hex-values.
`plot_colors` draws a plot showing the hex value of input and the corresponding actual color.

Example of picking three colors by their name and plotting them:

```{r example_colorsbyname}
mycolors <- colors_thl(c("thl.green", "ruby", "petrol"))
plot_colors(mycolors)
```


### Usage of color palettes

Color palettes define a group of colors which can be used together.

In `thlGraphs` there are three types of palettes depending on the use case.
Options are:

- sequence ("s1"..."s6): six different palettes, colors changing from lightr to darker
- diverging ("k1"..."k6): six different palettes, colors changing from one to another, having a light color in middle
- categorical ("quali", "line", "area"): three different palettes for marking different groups

`palette_thl` returns palette's hex-values of colors.
User selects name of the palette and  number of colors.


Example of picking six colors from a qualitative palette and plotting them:

```{r}
mypalette <- palette_thl(name = "quali", n = 6)
plot_colors(mypalette, nrow = 1)
```

Example of picking five colors from a series palette and plotting them:

```{r}
mypalette <- palette_thl(name = "s2", n = 5)
plot_colors(mypalette, nrow = 1)
```

Example of picking five colors from a diverging palette and plotting them:

```{r}
mypalette <- palette_thl(name = "k4", n = 5)
plot_colors(mypalette, nrow = 1)
```


### Usage of color sets

In addition to color palettes `thlGraphs` defines predefined color sets for categorizing groups.
These sets are predefined for meeting accessibility requirements.

There are two types of sets for both "line" and "area" type of plots.
These sets are defined for couples and triples of colors.

`colorset_thl` returns set's hex-values of colors.
User selects type of the set, number of colors in the set and serial number of the set.


For example plan is to make stacked bar chart and there are two different groups:

```{r}
colors <- colorset_thl(set = "area", n = 2, set_id = 1)
plot_colors(colors)
```

For example plan is to make line chart and there are three different groups:

```{r}
colors <- colorset_thl(set = "line", n = 3, set_id = 1)
plot_colors(colors)
```

