---
title: "thlGraphs Vignette"
author: "Petteri Mäntymaa, Tarja Palosaari, Salla Toikkanen, Oskari Luomala, Marianna Mukkulainen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)
library(thlGraphs)
```

## Demostration of THL's colors



There are five different types: ``main``, ``quali``, ``twoway``, ``quanti`` and ``powerpoint``.

</br>

Choosing colors by using ``thlColors`` function. Select number of colors, type and name of palette.

</br>

Example. Generate 3 colours from the quantitative color palette ``S2``.

```{r}
thlColors(n = 3, type = "quanti", name = "S2")
```

</br>

Displaying colors by using ``thlColorsDisplay`` function. There you can also select number of colors, type and name of palette as in ``thlColors`` function.

</br>

Example. Display 3 colors from the quantitative color palette ``S2``.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 3, type = "quanti", name = "S2")
```

## Type ``main`` - THL main colors



In type ``main`` is four different number of colors: 1, 2, 4 and 8. 

</br>

Example. Generate 2 colors from the main color.

```{r}
thlColors(n = 8, type = "main")
```


</br>

Example. Display 1 colors from the main color.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 1, type = "main")
```

</br>

Example. Display 2 colors from the main color.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 2, type = "main")
```

</br>


Example. Display 4 colors from the main color.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 4, type = "main")
```

</br>

Example. Display 8 colors from the main color.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 8, type = "main")
```

## Type ``quali`` - THL qualitative colours

THL qualitative colors in the order in which they should be used in line plots. There is 10 different number of colors.

</br>

Example of maximum colors. Generate 6 colors from the qualitative color palette color ``line``.

```{r}
thlColors(n = 6, type = "quali", name="line")
```

</br>

Example of maximum colors. Display 6 colors from the qualitative color palette color ``line``.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 6, type = "quali", name="line")
```

</br>

Example of maximum colors. Generate 10 colours from the qualitative color palette color ``bar``.

```{r}
thlColors(n = 10, type = "quali", name="bar")
```

</br>

Example of maximum colors. Display 10 colors from the qualitative color  palette color ``bar``.

```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 10, type = "quali", name="bar")
```

## Type ``quanti`` - THL quantitative colours

In type ``quanti`` you can choose six different names of palette: ``S1,S2,S3,... or S6``. Also you can choose from 1 to 7 number of colors. 

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S1``.
```{r}
thlColors(n = 7, type = "quanti", name="S1")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S1``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S1")
```

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S2``.
```{r}
thlColors(n = 7, type = "quanti", name="S2")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S2``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S2")
```

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S3``.
```{r}
thlColors(n = 7, type = "quanti", name="S3")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S3``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S3")
```

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S4``.
```{r}
thlColors(n = 7, type = "quanti", name="S4")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S4``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S4")
```

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S5``.
```{r}
thlColors(n = 7, type = "quanti", name="S5")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S5``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S5")
```

</br>

Example of maximum colors. Generate 7 colors from the quantitative color palette ``S6``.
```{r}
thlColors(n = 7, type = "quanti", name="S6")
```

</br>

Example of maximum colors. Display 1-7 colors from the quantitative color palette ``S6``.
```{r, fig.width=7}
thlColorsDisplay(n = 1:7, type = "quanti", name="S6")
```

## Type ``twoway`` - THL twoway quantitative colors

Using twoway quantitative color palettes

</br>

THL twoway color palette ``K1`` with 7 colors

</br>

Example of maximum colors. Generate 7 colors from the twoway quantitative color palette ``K1``.
```{r}
thlColors(n = 7, type = "twoway", name = "K1")
```

</br>

Displaying all different twoway palettes

</br>

Example of maximum colors. Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K1``.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7,9), type = "twoway", name = "K1")
```

</br>

Example of maximum colors.  Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K2``.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7,9), type = "twoway", name = "K2")
```

</br>

Example of maximum colors.  Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K3``.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7,9), type = "twoway", name = "K3")
```

</br>

Example of maximum colors.  Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K4``.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7,9), type = "twoway", name = "K4")
```

</br>

Example of maximum colors.  Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K5``.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7), type = "twoway", name = "K5")
```

</br>

Example of maximum colors.  Display 3, 5, 7 and 9 colors from the twoway quantitative color palette ``K6`.
```{r, fig.width=7}
thlColorsDisplay(n = c(3,5,7), type = "twoway", name = "K6")
```

## Type ``powerpoint``

Example of maximum colors. Generate 9 colors from the powerpoint color.
```{r}
thlColors(n = 9, type = "powerpoint") 
```

</br>

Example of maximum colors. Display 9 colors from the powerpoint color.
```{r, fig.width=7, fig.height=1}
thlColorsDisplay(n = 9, type = "powerpoint") 
```




## Demostration of THL's graphs



There are two different types: ``thlBarPlot``, ``thlLinePlot``.

</br>


Example of Bar plot. Barplot of monthly percentages (%) of patients treated over 180 days with caption year 2017. Data="yli180".
```{r, fig.width=7, fig.height=1}
data("yli180")
yli180$pros <- as.numeric(as.character(yli180$pros))
mycaption <- c(expression(paste(bold("Lähde:"), " THL")))  ## A caption which is partially in bold
thlBarPlot(data = subset(yli180, grepl("2017", kk)), xvar = kk, yvar = pros, ylimits = c(0,2), ylabel = "%", title = "Erikoissairaanhoidosssa yli 180 vrk odottaneet", caption = mycaption)
```

</br>


Cont...Example of Bar plot with horizontal mode.
```{r, fig.width=7, fig.height=1}
data("yli180")
yli180$pros <- as.numeric(as.character(yli180$pros))
mycaption <- c(expression(paste(bold("Lähde:"), " THL")))  ## A caption which is partially in bold
thlBarPlot(data = subset(yli180, grepl("2017", kk)), xvar = kk, yvar = pros, ylimits = c(0,2), ylabel = "%", title = "Erikoissairaanhoidosssa yli 180 vrk odottaneet", caption = mycaption, horizontal = TRUE)
```


</br>


Examples of Line plots. Data="yli180". Thl logo is included in the plot.


Default ilne plot. Data=yli90.
' ## Default line plot:
#' thlLinePlot(data = subset(dat, year<2007), xvar = year, yvar = value, 
#'                    groupvar = group, ylimits = c(0,350000))
```{r, fig.width=7, fig.height=1, echo=FALSE}
data("yli90")
yli90$AVI2<-factor(yli90$AVI, levels = yli90$AVI, labels = c("Etelä-Suomi","Lounais-Suomi","Itä-Suomi","Länsi- ja Sisä-Suomi", "Pohjois-Suomi", "Lappi"))
thlLinePlot(data = yli90, xvar = AVI2, yvar = `1/2018`, ylimits = c(0,700), ylab = "count",
title = "AVI Suomen eri osissa tammikuussa 2018",
caption="")
thlPlotLogo(label =NULL, x = .67, y = .04, size = 1, fontsize = 10)
```
, xaxis.breaks=c("Itä-Suomi", "Lappi")

```{r, fig.width=7, fig.height=1}
data("yli180")
yli180$kk2<-factor(yli180$kk, levels = yli180$kk)
thlLinePlot(data = yli180, xvar = kk2, yvar = pros, ylimits = c(0,2), ylab = "%",
title = "Erikoissairaanhoidosssa yli 180 vuorokautta hoitoa \nodottaneet kolmannesvuosittain 2015 - 2018",
caption="", xaxis.breaks = c("12/2015","12/2016","12/2017","12/2018"))
thlPlotLogo(label =NULL, x = .67, y = .04, size = 1, fontsize = 10)
```



